### 2011-08-15 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

\begin{table}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine & Windows \\
  Input data set & \texttt{100-500} \\
  Iterations & 20 \\
  \hline
  \end{tabular}
\end{table}

\begin{itemize}
	\item For each input file: how long does model creation take?
	\item How long does it take to communicate with GLPK? Creating the input / parsing the output.
	\item Which construction heuristic is the best - limit GLPK to like 1 second
	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?
	\item Which GLPK -> How does (time->quality) look, how does (input->time) look
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Fuzzy wins in every single case) - take note of quality (mean, variance) but also time (again, mean)
  \item Can FIDAX be improved by Hungry?
  \item Can we improve performance on huge data by ignoring textual content? Check for building as well as actual heu times.
\end{itemize}

>>>>

\begin{table}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine           & Windows \\
  Input data set    & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
  \end{tabular}
\end{table}

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \jmodule{Glpk} CH set to a time limit from 1 to 49 seconds with increments of 2 (25 settings * 20 iterations = 500 configurations in total). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights).\\

TODO input -> time dependency too

\subsection{Still to do}

\begin{itemize}
	\item For each input file: how long does model creation take?
	\item How long does it take to communicate with GLPK? Creating the input / parsing the output.
	\item Which construction heuristic is the best - limit GLPK to like 1 second
	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Fuzzy wins in every single case) - take note of quality (mean, variance) but also time (again, mean)
  \item Can FIDAX be improved by Hungry?
  \item Can we improve performance on huge data by ignoring textual content? Check for building as well as actual heu times.
\end{itemize}
